Visualize ukb whole genome, using ctwas results

### 2021-02-10 analysis/simulation-ctwas-ukbWG-gtex.adipose_s40.22.Rmd
match ctwas 0.1.10

```{r gene}
# p2 <- pow(niter, n, phenores[["batch"]][[1]][["sigma_beta"]], gene.p)
print(p2)
# save(p1,p2, file = "data/power_s80.45.Rd")
```

@@

```{r func}
plot_par <- function(configtag, tags){
  source(paste0(outputdir, "config", configtag, ".R"))
  phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
  susieIfs <- paste0(outputdir, runtag, "_simu", simutags, "_config", configtag, ".s2.susieIrssres.Rd")
  susieIfs2 <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".s2.susieIrss.txt")

  mtx <- show_param(phenofs, susieIfs, susieIfs2, thin = thin)
  par(mfrow=c(1,3))
  cat("simulations ", paste(tags, sep=",") , ": ")
  cat("mean gene PVE:", mean(mtx[, "PVE.gene_truth"]), ",", "mean SNP PVE:", mean(mtx[, "PVE.SNP_truth"]), "\n")
  plot_param(mtx)
}

plot_PIP <- function(configtag, tags){
   phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".susieIrss.txt")

@@

## ctwas_rss parameter estimation

```{r param1susie, fig.height=3, fig.width=8, message=F}
configtag <- 1

simutags <- paste(1, 1:5, sep = "-")
plot_par(configtag, simutags)
# plot_PIP(configtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, simutags)
# plot_PIP(configtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, simutags)
```

>>>>

```{r gene}
# p2 <- pow(niter, n, phenores[["batch"]][[1]][["sigma_beta"]], gene.p)
print(p2)
# save(p1,p2, file = "data/power_s40.22.Rd")
```

@@

```{r func}
plot_par <- function(configtag, runtag, simutags){
  source(paste0(outputdir, "config", configtag, ".R"))
  phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
  susieIfs <- paste0(outputdir, runtag, "_simu", simutags, "_config", configtag, ".s2.susieIrssres.Rd")
  susieIfs2 <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".s2.susieIrss.txt")

  mtx <- show_param(phenofs, susieIfs, susieIfs2, thin = thin)
  par(mfrow=c(1,3))
  cat("simulations ", paste(simutags, sep=",") , ": ")
  cat("mean gene PVE:", mean(mtx[, "PVE.gene_truth"]), ",", "mean SNP PVE:", mean(mtx[, "PVE.SNP_truth"]), "\n")
  plot_param(mtx)
}

plot_PIP <- function(configtag, runtag,  simutags){
   phenofs <- paste0(outputdir, "ukb-s40.22-adi", "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".susieIrss.txt")

@@

## Results-last step impact

After we have the estimated parameters, we obtain PIP for genes in one the following ways:
(1) run susie for each region using all SNPs
```{r param1-1, fig.height=3, fig.width=8, message=F, cache=T}
configtag <- 1
runtag2 = "config1_ctwas_rss_s3_full/ukb-s40.22-adi"

simutags <- paste(1, c(2,4,5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag2, simutags)

simutags <- paste(2, c(2,4), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag2, simutags)
```
(2) run susie for each region thinned SNPs 
```{r param1-2, fig.height=3, fig.width=8, message=F}
configtag <- 1
runtag2 = "config1_ctwas_rss_s3_thin/ukb-s40.22-adi"

simutags <- paste(1, c(2,4,5), sep = "-")
plot_PIP(configtag, runtag2, simutags)

simutags <- paste(2, c(2,4), sep = "-")
plot_PIP(configtag, runtag2, simutags)
```

(3) run susie for each regions with thinned SNPs, then select regions with strong gene PIP (max PIP > 0.8) and rerun susie with full SNPs.
```{r param1-3, fig.height=3, fig.width=8, message=F}
configtag <- 1
runtag2 = "ukb-s40.22-adi"

simutags <- paste(1, c(2,4,5), sep = "-")
plot_PIP(configtag, runtag, simutags)

simutags <- paste(2, c(2,4), sep = "-")
plot_PIP(configtag, runtag2, simutags)
```

## Results-more simulation settings
We run the last step of `ctwas_rss` using way (3) as described above.

```{r param2, fig.height=3, fig.width=8, message=F}

configtag <- 1
runtag = "ukb-s40.22-adi"

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(9, 1:4, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
```

### 2021-02-10 analysis/simulation-ctwas-ukbWG-gtex.adipose_s80.45.Rmd
match ctwas 0.1.10

```{r func}
plot_par <- function(configtag, tags){
  source(paste0(outputdir, "config", configtag, ".R"))
  phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
  susieIfs <- paste0(outputdir, runtag, "_simu", simutags, "_config", configtag, ".s2.susieIrssres.Rd")
  susieIfs2 <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".s2.susieIrss.txt")

  mtx <- show_param(phenofs, susieIfs, susieIfs2, thin = thin)
  par(mfrow=c(1,3))
  cat("simulations ", paste(tags, sep=",") , ": ")
  cat("mean gene PVE:", mean(mtx[, "PVE.gene_truth"]), ",", "mean SNP PVE:", mean(mtx[, "PVE.SNP_truth"]), "\n")
  plot_param(mtx)
}

plot_PIP <- function(configtag, tags){
   phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".susieIrss.txt")

@@

## ctwas_rss

```{r param1susie, fig.height=3, fig.width=8, message=F}
configtag <- 1

simutags <- paste(1, 1:5, sep = "-")
plot_par(configtag, simutags)
# plot_PIP(configtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, simutags)
# plot_PIP(configtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, simutags)
```

>>>>

```{r func}
plot_par <- function(configtag, runtag, simutags){
  source(paste0(outputdir, "config", configtag, ".R"))
  phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
  susieIfs <- paste0(outputdir, runtag, "_simu", simutags, "_config", configtag, ".s2.susieIrssres.Rd")
  susieIfs2 <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".s2.susieIrss.txt")

  mtx <- show_param(phenofs, susieIfs, susieIfs2, thin = thin)
  par(mfrow=c(1,3))
  cat("simulations ", paste(simutags, sep=",") , ": ")
  cat("mean gene PVE:", mean(mtx[, "PVE.gene_truth"]), ",", "mean SNP PVE:", mean(mtx[, "PVE.SNP_truth"]), "\n")
  plot_param(mtx)
}

plot_PIP <- function(configtag, runtag,  simutags){
   phenofs <- paste0(outputdir, "ukb-s80.45-adi", "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".susieIrss.txt")

@@

## Results-last step impact

After we have the estimated parameters, we obtain PIP for genes in one the following ways:
(1) run susie for each region using all SNPs
```{r param1-1, fig.height=3, fig.width=8, message=F, cache=T}
configtag <- 1
runtag2 = "config1_ctwas_rss_s3_full/ukb-s80.45-adi"

simutags <- paste(1, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag2, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
```
(2) run susie for each region thinned SNPs 
```{r param1-2, fig.height=3, fig.width=8, message=F}
configtag <- 1
runtag2 = "config1_ctwas_rss_s3_thin/ukb-s80.45-adi"

simutags <- paste(1, 1:5, sep = "-")
plot_PIP(configtag, runtag2, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_PIP(configtag, runtag2, simutags)
```

(3) run susie for each regions with thinned SNPs, then select regions with strong gene PIP (max PIP > 0.8) and rerun susie with full SNPs.
```{r param1-3, fig.height=3, fig.width=8, message=F}
configtag <- 1
runtag2 = "ukb-s80.45-adi"

simutags <- paste(1, 1:5, sep = "-")
plot_PIP(configtag, runtag2, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_PIP(configtag, runtag2, simutags)
```

## Results-more simulation settings
We run the last step of `ctwas_rss` using way (3) as described above.

```{r param2, fig.height=3, fig.width=8, message=F}

configtag <- 1
runtag = "ukb-s80.45-adi"

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(5, 2:3, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(7, 2:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(9, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
```

### 2021-02-10 analysis/simulation-ctwas-ukbWG-gtex.adipose_visual.Rmd
match ctwas 0.1.10

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message= F, warning = F)
```
Provide visualization for analysis [here]

```{r output dir}
outputdir <- "~/causalTWAS/simulations/simulation_ctwas_rss_20210112/"

@@

@@

## Simulation- high power

@@

```{r sim 1-3-17, out.width = "98%", out.height="95%"}
# TODO, thin option
chrom <- 1
runtag <- "ukb-s40.22-adi"
simutag <- "1-1"
configtag <- 1

susief <- paste0(outputdir, runtag, "_simu", simutag, "_config", configtag, ".s2.susieIrss.txt")
pf <- paste0(outputdir, runtag, "_simu",simutag)
phenof <- paste0(outputdir, runtag, "_simu", simutag, "-pheno.Rd")
plot_all(susief, pf, phenof, chrom)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message= F, warning = F)
```

```{r output dir}
outputdir <- "~/causalTWAS/simulations/simulation_ctwas_rss_20210117/"

@@

  if (thin !=1){
    b <- a[a$type == "gene" | (a$type == "SNP" & a$ifcausal == "Causal") | 
             (a$type == "SNP" & a$ifcausal == "Non causal" & rbinom(nrow(a), 1, thin) ==1)]
  }

@@

## Simulation

@@

```{r sim 2, out.width = "98%", out.height="95%"}
chrom <- 7
runtag <- "ukb-s80.45-adi"
simutag <- "2-1"
configtag <- 1

susief <- paste0(outputdir, runtag, "_simu", simutag, "_config", configtag, ".susieIrss.txt")
pf <- paste0(outputdir, runtag, "_simu",simutag)
phenof <- paste0(outputdir, runtag, "_simu", simutag, "-pheno.Rd")
plot_all(susief, pf, phenof, chrom, thin = 0.01)
```
